Towards Spherical Robots For Mobile Mapping In Human Made Environments\tnoteref{mytitlenote}

### 2021-05-13 Latex/sections/conclusion.tex
Added spherical robot renders

However, as \ref{sec:floatres} shows, some outliers remain due to the simplistic point-to-plane correspondence model, which is to be improved in future studies.
One idea to do so is to employ a local clustering technique onto the individual scans before registering them globally. 
Points from the scan with a similar normal get clustered together if their distance is small enough.
This way, a cluster represents a local plane while at the same time storing all the points that belong to that plane.
Point-to-plane correspondences then arise from the intersection of local clusters with global planes.

>>>>

However, as section~\ref{sec:experimentalSetup} shows, some outliers remain due to the simplistic point-to-plane correspondence model, which is to be improved in future studies.
One idea to do so is to employ a local clustering technique onto the individual scans before registering them globally. 
Points from the scan with a similar normal get clustered together if their distance is small enough.
This way, a cluster represents a local plane while at the same time storing all the points that belong to that plane.
Point-to-plane correspondences then arise from the intersection of local clusters with global planes.

### 2021-05-13 Latex/sections/simulation.tex
Added spherical robot renders

Figure~\ref{fig:simulatedDatasets} shows a noise-free trajectory through a simulated environment and a trajectory with noisy sensors.
In the noise-free case, the trajectory slightly bends in the direction of disturbance torque sideways while also varying in velocity in the intended direction of travel.
In the noisy case, the ideal straight trajectory is assumed.
Hence the planes enclosing the room are sensed multiple times. 
In particular, we see that the trajectory of the robot leads through one of the sensed planes. 
Also, the further the sensed points are, the noisier they appear, which is consistent with the larger influence of the pose error at higher distances.

\begin{figure*}
	\centering
	\includegraphics[width=0.51\textwidth]{images/perfect_bottom}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_bottom}\\
	\includegraphics[width=0.51\textwidth]{images/perfect_top}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_top}\\
	\includegraphics[width=0.51\textwidth]{images/perfect_top_view}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_top_view}\\\vspace{0.5cm}
	\includegraphics[width=0.25\textwidth]{images/sim_frame_00.png}\hfill
	\includegraphics[width=0.25\textwidth]{images/sim_frame_02.png}\hfill
	\includegraphics[width=0.25\textwidth]{images/sim_frame_06.png}\hfill
	\includegraphics[width=0.25\textwidth]{images/sim_frame_08.png}
	\caption{Two simulated datasets of a long hallway of size $\SI{4}{\meter}\times\SI{3}{\meter}\times\SI{100}{\meter}$. Ideal noise free (left), noisy pose ($\mathcal{N}_\varphi = \mathcal{N}_\psi(\mu = 0.0001, \sigma= 0.00001)$) and noisy range measurements ($\mathcal{N}_r(\mu = 0, \sigma = 0.001)$) (right). Below: Initial sequence of the simulation of the ideal dataset showing the simulated motion of the robot.}
	\label{fig:simulatedDatasets}
\end{figure*}

>>>>

Figure~\ref{fig:simulatedDatasets} shows a noise-free trajectory through a simulated environment and a trajectory with noisy sensors while figure~\ref{fig:robotRender} shows a rendering of the simulated robot as well as the simulation sequence. 
In the noise-free case, the trajectory slightly bends in the direction of disturbance torque sideways while also varying in velocity in the intended direction of travel.
In the noisy case, the ideal straight trajectory is assumed.
Hence the planes enclosing the room are sensed multiple times. 
In particular, we see that the trajectory of the robot leads through one of the sensed planes. 
Also, the further the sensed points are, the noisier they appear, which is consistent with the larger influence of the pose error at higher distances.

\begin{figure*}
	\centering
	\includegraphics[width=0.51\textwidth]{images/perfect_bottom}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_bottom}\\
	\includegraphics[width=0.51\textwidth]{images/perfect_top}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_top}\\
	\includegraphics[width=0.51\textwidth]{images/perfect_top_view}\hfill
	\includegraphics[width=0.48\textwidth]{images/noisy_pose_and_range_top_view}
	\caption{Two simulated datasets of a long hallway of size $\SI{4}{\meter}\times\SI{3}{\meter}\times\SI{100}{\meter}$. Ideal noise free (left), noisy pose ($\mathcal{N}_\varphi = \mathcal{N}_\psi(\mu = 0.0001, \sigma= 0.00001)$) and noisy range measurements ($\mathcal{N}_r(\mu = 0, \sigma = 0.001)$) (right).}
	\label{fig:simulatedDatasets}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.5\textwidth]{images/sim_frame_00.png}\hfill
	\includegraphics[width=0.5\textwidth]{images/sim_frame_02.png}\\
	\includegraphics[width=0.5\textwidth]{images/sim_frame_06.png}\hfill
	\includegraphics[width=0.5\textwidth]{images/sim_frame_08.png}\\\vspace{0.5cm}
	\includegraphics[width=0.5\textwidth]{images/ProtoRoll1.png}\hfill
	\includegraphics[width=0.5\textwidth]{images/ProtoRoll2.png}
	\caption{Top: Initial sequence of the simulation of the ideal dataset showing the simulated motion of the robot.
	Below: Rendering of the simulated robot, a Livox laser scanner insider a spherical shell.}
	\label{fig:robotRender}
\end{figure*}
